Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-11 inst/examples/20160715-slides-Krakow.Rmd
s
sa

sivu 12. Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata mitkä vuodet highlightataan. Tällaisena ei vielä toimi.

@@

**How?** By combining library catalogues (Fennica, Kungliga, ESTC, CERL)

@@

[Intro]

@@

- Open source tools for library catalogues (Github)

@@

[Intro]

### Context

- Finnish knowledge production 1640-1828 can only be understood in the Swedish context.

- Academy of Turku as part of the Swedish University system is the centre of Finnish knowledge production.

### Challenges: nationally delineated perspectives by using nationally collected materials

### Outline of the presentation

1) Big picture & political events

@@

### 1. Big Picture & Political Events

@@

[Big Picture & Political Events]

@@

[Big Picture & Political Events]

### Stockholm & political events

@@

TODO: Vaihdettiin tähän Stockholm, riittää julkaisumäärät. Miksi katalogina lukee Fennica?

@@

### 2. Publishers

@@

[Publishers]

@@

### Development of use of different languages in Finnish National Bibliography

```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
catalogue <- "Fennica"
df <- df0
langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  # Classify a document to the specifed language
  # If document is assigned with languages, each case is considered
  # so one doc may have multiple entries corresponding to different languages
  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
  # Combine data frames for specified languages
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# ----------------------------------

df <- dfl %>% filter(catalog == catalogue)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
                 paper = sum(paper.consumption.km2, na.rm = TRUE))

# TITLE COUNT
p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Title count (n)") +
       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
print(p)

@@

p <- ggplot(df, aes(x = publication_decade, y = duplicates, fill = catalog)) +
       geom_bar(position = "dodge", stat = "identity") +
       ylab("Duplicates (%)") +
       scale_fill_manual(values = c("blue", "red")) + 
       ggtitle(paste("Duplicates", paste(range(na.omit(df$publication_decade)), collapse = "-")))

>>>>

sivu 12. Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata mitkä vuodet highlightataan. Tällaisena ei vielä toimi. Onhan katalogi oikein?

@@

**How?** By combining library catalogues (Fennica, Kungliga, ESTC, CERL's HPB database)

@@

@@

- Open source tools for library catalogues (Github/Fennica)

@@

### Outline of Quantitative Study of Finnish Knowledge Production, 1640-1828

1) General trends & political events

@@

### 1. General trends & political events

@@

[General trends & political events]

@@

[General trends & political events]

### Stockholm & democratic cycles

@@

TODO: Vaihdettiin tähän Stockholm, riittää julkaisumäärät. Miksi katalogina lukee Fennica? Pitää olla Kungligan mukaan data tässä.

@@

### 2. Publishers in Sweden and Turku

@@

[Publishers in Sweden and Turku]

@@

@@

p <- ggplot(df, aes(x = publication_decade, y = duplicates, fill = catalog)) +
       geom_bar(position = "dodge", stat = "identity") +
       ylab("Duplicates (%)") +
       scale_fill_manual(values = c("blue", "red")) + 
       ggtitle(paste("Certain duplicates Fennica-Kungliga", paste(range(na.omit(df$publication_decade)), collapse = "-")))
